\FloatBarrier
\section{Discussion}
\label{sec:discussion}

\paragraph{The hypothesis-dropping pattern.}
The actor--critic case is not isolated. Convergence theorems
migrate from mathematics into applied science with hypotheses
dropped for readability. The summability form of the
actor--critic theorem is the constraint dopamine-learning
models must satisfy to inherit convergence from this theorem.
Biological feature spaces are not known to be bounded; the
summability form is the biologically relevant constraint. The
pattern applies broadly: any scientific claim that cites a
formal theorem as authority inherits the theorem's hypotheses,
and those hypotheses are rarely re-checked in downstream prose.

\paragraph{Complementarity of verification layers.}
The mutation-kill matrix (Fig.~\ref{fig:mutation}) shows that no
single verification modality catches every failure mode. The Lean
proof catches structural errors (wrong convergence rate, missing
hypothesis, vacuous closure). The simulation catches parametric
errors (wrong $\lambda$ range, wrong credit-window width). The
property tests catch numerical invariant violations at concrete
parameter values. The sandwich bound across all three layers is
non-redundant: every pair of layers leaves at least one mutation
uncovered. This motivates a multi-layer verification architecture
rather than relying on any single modality.

\paragraph{The \sys{} fleet as a verification tool.}
\sys{} is a multi-agent research fleet, not a single autonomous
agent. The fleet surfaced the counterexample to I5a via
\textsc{Aristotle}, the Kairos orchestrator proposed the corrected
statement, and the Lean kernel verified it. The per-animal
re-analysis and the pairwise distinguishability matrix were
produced by the simulation and calibration agents. The pipeline
is reusable: it applies wherever a scientific claim inherits a
formal guarantee from a cited theorem. The four-paradigm
transfer (Tang, Sousa, Greenstreet, Markowitz) demonstrates this
portability: the same infrastructure verifies rules from four
independent labs without modification.

\paragraph{Broader impact.}
Dopamine-dependent credit assignment governs how the brain
attributes outcomes to past actions. Computational models of
this process inform drug development for addiction and
Parkinson's disease, closed-loop brain stimulation protocols,
and reward-based training of artificial agents. A formal
refutation of a commonly-cited convergence guarantee (TD(0)
as an account of the seconds-scale credit window) changes which
models downstream applications can safely rely on. The corrected
actor--critic theorem provides a stronger foundation.

\paragraph{Limitations.}
The main convergence theorems (TD(0), SARSA(0), TD($\lambda$))
are proved modulo a shared increment-summability lemma that
encodes the Robbins--Monro stochastic-approximation theorem,
pending upstream Mathlib formalization. Two Vogels--Sprekeler
theorems were found to be false as stated and corrected.
The simulation is calibrated on public data from one lab.
The DAT-KO prediction has not yet been tested experimentally.
The classifier's Hoeffding bound requires $n \ge 18$ independent
observations per paradigm, which limits applicability to
small-sample regimes.
